NON-London

### 2017-06-27 LowUseEngland.Rmd
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.
Final Pre Blog
Last update before publsihing the 3rd blog

CumbriaStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

(218977.5-  184071.4 )/184071.4

@@

CornStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

@@

SuffStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

@@

 HullStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

HullStrap <- ValueTtest(HullStrap)

>>>>

CumbriaStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Cumbria", y = "% difference from expected")
SaveFig("CumbriaDistributionPlot.png")

@@

z <- ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>% MakeLeaflet(.)
z
saveWidget(z, file=file.path(gitpage, "CumbriaLowUse.html"), selfcontained = TRUE )

@@

CornStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Cornwall", y = "% difference from expected")
SaveFig("CornwallDistributionPlot.png")

@@

z <- MakeLeaflet(Cornwall)
z
saveWidget(z, file=file.path(gitpage, "CornwallLowUse.html"), selfcontained = TRUE )

@@

SuffStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Coastal Suffolk", y = "% difference from expected")
SaveFig("CoastSuffDistributionPlot.png")

@@

z <- MakeLeaflet(CoastWave)
z
saveWidget(z, file=file.path(gitpage, "CoastSuffLowUse.html"), selfcontained = TRUE )

@@

 HullStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Cumbria", y = "% difference from expected")
SaveFig("HullDistributionPlot.png")

HullTtest <- ValueTtest(HullStrap)

z <- MakeLeaflet(Hull)
z
saveWidget(z, file=file.path(gitpage, "HullLowUse.html"), selfcontained = TRUE )
